---
title: "Creating a cross stitch"
author: "Haoying Shen"
date: "31/10/2020"
output: pdf_document
---

```{r, include=FALSE}
library(imager)
library(tidyverse)
library(tidymodels)
library(sp)
library(scales)
library(cowplot)
library(dmc)
change_resolution <- function(image_df, x_size)
{
  ## change_resolution(image_df, x_size) subsamples an image to produce
  ## a lower resolution image. Any non-coordinate columns in the data
  ## frame are summarized with their most common value in the larger
  ## grid cell.
  ##
  ## Input:
  ## - image_df: A data frame in wide format. The x-coordinate column MUST
  ##             be named 'x' and the y-coordinate column MUST be named 'y'.
  ##             Further columns have no naming restrictions.
  ## - x_size:   The number of cells in the x-direction. The number of cells
  ##             in the vertical direction will be computed to maintain the 
  ##             perspective. There is no guarantee that the exact number
  ##             of cells in the x-direction is x_size
  ##
  ## Output:
  ## - A data frame with the same column names as image_df, but with fewer 
  ##   entries that corresponds to the reduced resolution image.
  ##
  ## Example:
  ##   library(imager)
  ##   library(dplyr)
  ##   fpath <- system.file('extdata/Leonardo_Birds.jpg',package='imager') 
  ##   im <- load.image(fpath)
  ##   im_dat<- as.data.frame(im,wide = "c") %>% rename(R = c.1, G = c.2, B = c.3) %>%
  ##            select(x,y,R,G,B)
  ##   agg_image <- change_resolution(im_dat, 50)
  
  if(!require(sp)) {
    stop("The sp packages must be installed. Run install.packages(\"sp\") and then try again.")
  }
  if(!require(dplyr)) {
    stop("The dplyr packages must be installed. Run install.packages(\"dplyr\") and then try again.")
  }
  
  sp_dat <- image_df 
  gridded(sp_dat) = ~x+y
 
  persp = (gridparameters(sp_dat)$cells.dim[2]/gridparameters(sp_dat)$cells.dim[1])
  y_size = floor(x_size*persp)
  orig_x_size = gridparameters(sp_dat)$cells.dim[1]
  orig_y_size = gridparameters(sp_dat)$cells.dim[2]
  
  x_res = ceiling(orig_x_size/x_size)
  y_res = ceiling(orig_y_size/y_size)
  
  gt = GridTopology(c(0.5,0.5), c(x_res, y_res),
                    c(floor(orig_x_size/x_res), floor(orig_y_size/y_res)))
  SG = SpatialGrid(gt)
  agg = aggregate(sp_dat, SG, function(x) names(which.max(table(x)))[1] )
  agg@grid@cellsize <- c(1,1)
  df <- agg %>% as.data.frame %>% rename(x = s1, y = s2)  %>% select(colnames(image_df))
  
  return(df)
}
  
process_image <- function(image_file_name, k_list){
  ## process_image(image_file_name, k_list) takes a image and a few values to create
  ## a k means cluster. Includes information on the clustering data, k mean centers
  ## as well as RGB/ DMC values.
  ##
  ## Input:
  ## - image_file_name: any PNG/JPG image
  ## - k_list: a list of integers to act as number of clusters.
  ##
  ## Output:
  ## - a list that includes k clustering data for each of the integers in k_list,
  ## dataframes with RGB/DMC values, and a dataframe in wide format.
  ##
  ## Example:
  ## im <- imager::load.image("C:/Users/haoyi/Desktop/MS.png")
  ## k_list = c(3, 5, 7)
  ##cluster_info <- process_image(im, k_list)
  tidy_dat <- as.data.frame(image_file_name, wide = "c") %>% rename(R = c.1, G = c.2, B = c.3)
  clustdata <- tibble(k_list) %>%
  mutate(
  kclust = map(k_list, ~kmeans(select(tidy_dat,c(-x,-y)), centers = .x, nstart = 6)),
  glanced = map(kclust, glance),
  )
  centres <- list()
  b = 1
  for(i in clustdata$kclust)
  {
    centres[[b]] <- tidy(i)
    centres[[b]] <- centres[[b]] %>% mutate(col = rgb(R,G,B))
    b = b+1
  }
  j = 1
  while(j < length(centres) + 1)
  {
    temp <- list()
    z <- 1
    for(n in centres[[j]]$col)
    {
      temp[z] <- dmc(n)$name
      z = z+1
    }
    dmc_n <- unlist(temp)
    centres[[j]]$name <- c(dmc_n)
    j = j + 1
  }
  
  data <- list(clustdata, centres, tidy_dat) 
}
  
  scree_plot <- function(cluster_info){
  ## scree_plot(cluster_info) takes cluster_info, which is the output of process_image
  ## and uses the data to create a scree_plot which plots the values in k_list on x-axis
  ## and the corresponding tot.withinss(Total within-cluster sum of squares) value
  ##
  ## Input:
  ## - cluster_info, the list of dataframes obtained from process_image
  ##
  ## Output:
  ## - plots a scree_plot based on K-list and tot.withinss
  ##
  ## Example:
  ## im <- imager::load.image("C:/Users/haoyi/Desktop/MS.png")
  ## k_list = c(3, 5, 7)
  ## cluster_info <- process_image(im, k_list)
  ## scree_plot(cluster_info)
  within_list <- list()
  x = 1
  for(i in cluster_info[[1]]$glanced){
    within_list[x] <- i$tot.withinss
    x = x + 1
  }
  withinss <- unlist(within_list)
  
  ggplot(cluster_info[[1]], aes(k_list, withinss)) +
  ggtitle( "Scree-plot for the given values in k_list")+
  ylab("tot.withinss") + xlab("k")+
  geom_line() +
  geom_point() 
  }
  
  colour_strips <- function(cluster_info){
  ## colour_strips(cluster_info) takes cluster_info, which is the output of process_image
  ## and uses the RGB data within to create color strips
  ##
  ## Input:
  ## - cluster_info, the list of dataframes obtained from process_image
  ##
  ## Output:
  ## - creates a color strip for each value different clustering in k_list based on 
  ## RGB data
  ##
  ## Example: 
  ## im <- imager::load.image("C:/Users/haoyi/Desktop/MS.png")
  ## k_list = c(3, 5, 7)
  ## cluster_info <- process_image(im, k_list)
  ## colour_strips(cluster_info)
  for (i in cluster_info[[2]])
  show_col(i$col)
}
  
make_pattern <- function(cluster_info, k, x_size, black_white, background_colour = NULL){
  ## make_pattern(cluster_info, k, x_size, black_white, background_colour = NULL) 
  ## creates a cross stitch based on cluster_info, and a chosen clustering k(from k_list)
  ## changes the resolution based on x_size, which is the number of stitches in the 
  ## x-direction. The stitched pattern can be in color or black and white, based on the
  ## boolean black_white. Finally, the back_ground color can be removed from the stitch
  ## by inputting the hex string, by default this is NULL and the background will not be
  ## removed
  ##
  ## Input:
  ## - cluster_info: the output of process_image, holds the data on the RGB values of the
  ## original image as well as the clustered data
  ## - k: the chosen k value from k_list.
  ## - x_size: the number of desired stitches in the x-direction
  ## - black_white: a boolean that determines if the stitch will include color or not.
  ## - background_colour: removes the color from the stitch based on an inputted RGB
  ##   hex code, by default this is NULL.
  ##
  ## Output:
  ## - A cross stitch with a legend that includes a legend based on what color to stitch.
  ## The image will be based on the parameters above
  ##
  ## Example:
  ## im <- imager::load.image("C:/Users/haoyi/Desktop/MS.png")
  ## k_list = c(3, 5, 7)
  ## cluster_info <- process_image(im, k_list)
  ## make_pattern(cluster_info, 7, 40, TRUE)
  g = 1
  while(g < length(cluster_info[[1]]) + 1)
  {
    if(k == cluster_info[[1]]$k_list[[g]])
      img <- augment(cluster_info[[1]]$kclust[[g]], cluster_info[[3]]) %>% rename(cluster= .cluster)
      sub <- cluster_info[[2]][[g]]
      g=g+1
  }
  new_res <- change_resolution(img, x_size)
  
  if(is.null(background_colour) == FALSE){
    sub$cluster[sub$col == background_colour] <- NA
    sub$col[sub$col == background_colour] <- NA
    print(sub)
    print(cluster_info[[2]])
  }
  
  if(black_white == FALSE){
    ggplot(new_res, aes(x=x, y = y), color = factor(cluster), shape = factor(cluster)) +
    geom_point(aes(col = factor(cluster), shape = factor(cluster))) +
      scale_colour_manual(name = "Color to Stitch",
                          values = sub %>% select(cluster, col) %>% deframe,
                        label =  sub %>% select(cluster, name) %>% deframe)+
      scale_shape_manual(name = "Color to Stitch",
                         values = sub %>% select(cluster) %>% deframe,
                         label = sub %>% select(cluster, name) %>%deframe)+
    scale_y_reverse() + theme_void() +
      background_grid()
  }
  
  
  else{
    ggplot(new_res, aes(x=x, y = y)) +
    geom_point(aes(shape = factor(cluster))) +
    labs(shape = "Color to Stitch") +
      scale_colour_manual(name = "Color to Stitch",
                          values = sub %>% select(cluster, col) %>% deframe,
                        label =  sub %>% select(cluster, name) %>% deframe)+
      scale_shape_manual(name = "Color to Stitch",
                         values = sub %>% select(cluster) %>% deframe,
                         label =  sub %>% select(cluster, name) %>%deframe)+
    scale_y_reverse() + theme_void() +
      background_grid()
  }
}

```

This vignette will cover the functions used in creating a cross stitch template from a image.

##Creating Cluster_Info

The first function that will be covered is process_image, but before that we must save a image to a variable
```{r}
im <- imager::load.image("C:/Users/haoyi/Desktop/MS.png")
plot(im)
```

So this is the image that we want to turn into a cross stitch template.

```{r, message=FALSE}
set.seed(7)
k_list = c(3, 5, 7, 9, 20)
cluster_info <- process_image(im, k_list)
```
    
process_image generates many different dataframes which include information such as the k-means clustering information for the image from each of the values in k_list, as well as the RGB values which will be used to create the overall color of the image. Additionally this also includes the respective DMC name, which is the matching tread color for the stitch.

##Creating a Scree_plot

since eventually we want to figureout the best clustering value, we should use a scree_plot, this plots the total within sum of squares against each of the k values in k_list.
```{r}
scree_plot(cluster_info)
```
This is used to find the number of clusters that can explain most of the variance, or in our case create the most detailed picture. Screeplots almost exclusively decrease with more clusters. However this may be more harmful than beneficial, so we should go with the number that explains a good portion and does not rely on too many clusters. in this case the we see very little difference between 9 and 20 clusters, which shows that there is diminishing value. So 9 should be sufficient.


##Creating colorstrips

A good way to visualize what colours would be used for your given choice of k is to use the color_strips function. This will show you all of the colors that can be used to create the cross stitch for each k in k_list.
```{r}
colour_strips(cluster_info)
```
This further backs up the diminishing value of having more clusters, as we can see in the 20 cluster colorstrip there are many colors that are hard to distinguish from eachother. so choosing a lower number would get rid of that inefficiency by grouping those colors together.


##Creating the cross stitch

Finally we get to the cross stitching part, here we have many different options. the first input is cluster_info, the second is your chosen k-value, keep in mind this must be the same as a value within k_list. For the first one I will choose k = 7
```{r}
make_pattern(cluster_info, 7, 40, FALSE)
```
This next one uses 5 clusters instead, as you can see there are less colour choices
```{r}
make_pattern(cluster_info, 5, 40, FALSE)
```

we can also change the resolution of the final picture by changing x_value, the previous were done using 40, lets try with 100

```{r}
make_pattern(cluster_info, 7, 100, FALSE)
```

In this case the picture is far more detailed.

Lastly, the picture can be cross stitched in black and white when the input for black_white is turned to TRUE, and the symbol will be the only differentiation between the stitches.
```{r}
make_pattern(cluster_info, 7, 40, TRUE)
```